A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-17 paper/paper.Rnw
Fix brand plot

top_brands <- df_shoes %>%
  group_by(brand) %>%
  summarize(n = n()) %>%
  arrange(desc(n))

df_summ <- filter(df_shoes, brand %in% head(top_brands$brand, 8)) %>%
  group_by(brand) %>%
  summarize(n = n(),
            bowtie = sum(bowtie)/n, chevron = sum(chevron)/n,
            circle = sum(circle)/n, line = sum(line)/n,
            polygon = sum(polygon)/n, quad = sum(quad)/n,
            star = sum(star)/n, text = sum(text)/n, triangle = sum(triangle)/n)

df_summ_long <- df_summ %>%
  gather(key = shape, value = prop, -brand, -n) %>%
  arrange(brand)

df_summ_long$brand <- as.factor(df_summ_long$brand)
df_summ_long$shape <- factor(df_summ_long$shape, levels = classes)

# # Line plot
# ggplot(df_summ_long) + geom_point(aes(x = prop, y = shape, color = brand)) +
#   geom_path(aes(x = prop, y = shape, group = brand, color = brand)) +
#   ggtitle("Shape proportions by brand")

# unicode_symbols <- c(bowtie = "\u26FB", chevron = "\uFE3D",
#                      circle =  "\u23FA", line = "\u2225",
#                      polygon = "\u2B23", quad = "\u25A0",
#                      star = "\u2605", text = "a", triangle = "\u25BC",
#                      other = "\u003F")

ggplot(df_summ_long, aes(x = brand, y = prop, shape = factor(shape),
                         color = factor(shape))) +
  geom_point(size = 4) +
  scale_shape_manual(values = c("\u26FB","\uFE3D","\u23FA","\u2225",
                                "\u2B23","\u25A0","\u2605","a","\u25BC")) +
  theme_bw() +
  theme(legend.position = "none") +
  coord_flip() +
  ggtitle("Proportion of labeled shoes containing each shape by brand")
@

<<brands-within-shapes, fig.cap = "Caption here">>=
shapes <- lapply(X = classes, function(x){
  out <- df_shoes[df_shoes[,x, drop = T],]
  out$shape <- x
  out
})
names(shapes) <- classes

shapes %>% map_dfr(., function(x) {
  x %>% group_by(brand) %>%
    summarize(n = n()) %>%
    arrange(desc(n)) %>%
    mutate(prop = n / sum(n),
           shape = x$shape[1:length(n)]) %>%
    head(10)
  }) %>%
  ggplot() +
  geom_text(aes(x = as.factor(shape),
                               y = prop, label = brand,
                               color = as.factor(shape))) +
  theme(legend.position = "none")
@

>>>>

df_shoes_long <- df_shoes %>%
  tidyr::gather(key = feature, value = value, -str, -brand) %>%
  ungroup() %>%
  tidyr::nest(c(str, value)) %>%
  mutate(n_true = purrr::map_int(data, ~sum(.$value)),
         n_shoes_brand = purrr::map_int(data, ~length(.$value)))

brand_prop_by_feature <- df_shoes_long %>%
  group_by(feature) %>%
  mutate(prop = n_true/sum(n_true)) %>%
  arrange(feature, desc(prop)) %>%
  mutate(brand_cat = ifelse(row_number() <= 10, brand, "other")) %>%
  group_by(feature) %>%
  mutate(rank = pmin(row_number(), 11))
brand_prop_by_feature_10 <- brand_prop_by_feature %>%
  group_by(feature, brand_cat, rank) %>%
  summarize(prop = sum(prop)) %>%
  ungroup() %>%
  group_by(feature) %>%
  arrange(feature, rank) %>%
  mutate(cprop = cumsum(prop),
         cprop2 = lag(cprop, 1, default = 0),
         mid = (cprop + cprop2)/2,
         rank = ifelse(rank == 11, NA, rank))

ggplot(data = brand_prop_by_feature_10) +
  geom_bar(aes(x = feature, y = prop, fill = factor(rank)), position = "stack", stat = "identity", color = "black") +
  geom_text(aes(x = feature, y = 1-mid, label = brand_cat), data = filter(brand_prop_by_feature_10, prop > .05), size = 3) +
  scale_fill_brewer(palette = "Paired", guide = F, na.value = "grey") +
  scale_y_continuous("Proportion") + scale_x_discrete("") +
  ggtitle("Proportion of Labeled Features by Brand")
@
